### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/2.tex
min progress

@@

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Cpolymerwt_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Cpolymerwt_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Dnozzlem_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Dnozzlem_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Lm_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Lm_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Phi0V_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Phi0V_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Qm3s_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Qm3s_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_vstagems_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_vstagems_vs_Dfiberm}
\end{figure}

>>>>

Measurements were validaded with Camillo's, Gupta's, Jiang's, Min's, Sun's, Wang's, and Xue's \cite{Camillo2013, Gupta2007, Jiang2018, Min2013, Sun2006a, Wang2015, Xue2014} results as those authors reported both, a SEM image and the measured fiber diameter. For instance, Figure \ref{fig:imageAnalysisToolValidation} shows in white the reported diameters by Min and in blue the diameters measured by the \emph{Python script}. The measurement error of the developed script is about $3.2\%$ in avg. It is considerable to mention that the reported measurement error is mainly contributed to the fact that most fibers are not of the same diameter along the fiber length. In most cases, measurements at the end of the fibers are thicker than the ones measured u¿in the center.

\begin{figure}[!th]
\centering
\includegraphics[scale=0.8]{./Figures/imageAnalysisToolValidation.png}
\decoRule
\caption[Validation of the developed image analysis meassurement tool]{{Validation of the developed image analysis meassurement tool. SEM images of Min's work are used as an example. \cite{Min2013}}}
\label{fig:imageAnalysisToolValidation}
\end{figure}

@@

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Cpolymerwt_vs_Dfiberm.png}
\decoRule
\caption[Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Results]{Scatter Plot of Polymer Concentrations and Fiber Diameters from Literature Results. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Cpolymerwt_vs_Dfiberm}
\end{figure}

The trend of Figure \ref{fig:plt_Dnozzlem_vs_Dfiberm} shows that thicker nozzle diameters yield thicker fibers. However, the final fiber diameter can be reduced without changing the nozzle diameter. For instance Chang et al. \cite{Chang2008} achieved the thinnest fibers of about $50 nm$ in diameter even though Chang implemented nozzle needles of similar diameter as Shin, Min and Xu. \cite{Shin2019, Min2013, Xu2014}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Dnozzlem_vs_Dfiberm.png}
\decoRule
\caption[Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Results]{Scatter Plot of Nozzle Inner Diameters and Fiber Diameters from Literature Results. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Dnozzlem_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Lm_vs_Dfiberm.png}
\decoRule
\caption[Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Results]{Scatter Plot of NFES Working Distances and Fiber Diameters from Literature Results. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Lm_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Phi0V_vs_Dfiberm.png}
\decoRule
\caption[Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Results]{Scatter Plot of NFES Applied Voltages and Fiber Diameters from Literature Results. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Phi0V_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Qm3s_vs_Dfiberm.png}
\decoRule
\caption[Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Results]{Scatter Plot of Polymer Solution Flow Rates and Fiber Diameters from Literature Results. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Qm3s_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_vstagems_vs_Dfiberm.png}
\decoRule
\caption[Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Results]{Scatter Plot of Collector xy Stage Velocities and Fiber Diameters from Literature Results. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_vstagems_vs_Dfiberm}
\end{figure}
